Output Summary

### 2023-04-19 03-post-process/compare-sim-to-obs.Rmd

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "siw"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 0.5
    input: numeric
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Observed vs. Simulated Year Comparison"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`"
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output:
   html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 0.5
    input: numeric
editor_options: 
  chunk_output_type: console
---

### 2023-04-19 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd

>>>>

### Realized & BH

The blue shows the time series with variability explained only by Beverton-Holt dynamics.

```{r phi_E_Pb_dot-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])

  # draw on the posterior time series that includes BH prediction only
  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot[year,pop]", year = ts_yrs, pop = j)),
              yrs = all_yrs[ts_yrs])
}

### Realized & [BH + AR(1)]

The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.

```{r phi_E_Pb_dot2-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])

  # draw on the posterior time series that includes BH prediction and the carry over residual from last year
  # draw on the posterior time series that includes BH prediction only
  add_tseries(post_summ(post, sub_index("^phi_E_Pb_dot2[year,pop]", year = ts_yrs, pop = j)),
              yrs = all_yrs[ts_yrs])
}

### 2023-04-19 03-post-process/output-plots-children/10-rho-params.Rmd

# draw on the prior distribution
rho_pr = post_summ(post, "rho_Lphi_Ma_O0_pr[2,1]", probs = c(0.025, 0.1, 0.25, 0.75, 0.9, 0.975))
rect(rho_pr["2.5%",], usr[3], rho_pr["97.5%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
rect(rho_pr["10%",], usr[3], rho_pr["90%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
rect(rho_pr["25%",], usr[3], rho_pr["75%",], usr[4], col = scales::alpha("grey25", 0.15), border = NA)
abline(v = 0, lty = 2)

# param = rownames(rho_mean_out)[4]
# at_mp = mp[4,]
pop_rhos = function(param, at_mp) {

  # if the process is not one of the hydropower migration survival ones, do this
  # those processes are correlated across origins, because all populations share the same values each year
  if (!(param %in% c("rho_Lphi_Ma_O0", "rho_Lphi_Rb_Ra"))) {
    x = post_summ(post, paste0(param, vcov_inds), probs = c(0.1, 0.25, 0.75, 0.9))
    y = at_mp + runif(6, -0.4, 0.4)
    points(y ~ x["mean",], col = "salmon", pch = 3, lwd = 1.5)
    segments(x["25%",], y, x["75%",], y, col = scales::alpha("salmon", 0.5))
  } 
}

junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = scales::alpha("royalblue", 0.55))
segments(rho_mean_out[,"10%"], mp, rho_mean_out[,"90%"], mp, col = scales::alpha("royalblue", 0.55))
points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "royalblue", lwd = 3)

>>>>

box_upr = mp - rbind(diff(mp)/2, NA)
box_lwr = mp + rbind(diff(mp)/2, NA)
box_upr[nrow(box_upr),] = box_upr[nrow(box_upr)-1,] + diff(box_upr[1:2])
box_lwr[nrow(box_lwr),] = box_lwr[nrow(box_upr)-1,] + diff(box_lwr[1:2])

# draw on the prior distribution for rho
draw_rho_prior = function(param, box_lwr, box_upr) {
  rho_pr = post_summ(post, paste0(param, "_pr[2,1]"), probs = c(0.025, 0.1, 0.25, 0.75, 0.9, 0.975))
  rect(rho_pr["2.5%",], box_lwr, rho_pr["97.5%",], box_upr, col = scales::alpha("grey25", 0.15), border = NA)
  rect(rho_pr["10%",], box_lwr, rho_pr["90%",], box_upr, col = scales::alpha("grey25", 0.15), border = NA)
  rect(rho_pr["25%",], box_lwr, rho_pr["75%",], box_upr, col = scales::alpha("grey25", 0.15), border = NA)
  abline(v = 0, lty = 2)
}

pop_rhos = function(param, at_mp) {

  # if the process is not one of the hydropower migration survival ones, do this
  # those processes are correlated across origins, because all populations share the same values each year
  if (!(param %in% c("rho_Lphi_Ma_O0", "rho_Lphi_Rb_Ra"))) {
    x = post_summ(post, paste0(param, vcov_inds), probs = c(0.1, 0.25, 0.75, 0.9))
    y = at_mp + runif(6, -0.4, 0.4)
    points(y ~ x["mean",], col = "royalblue", pch = 3, lwd = 1.5)
    # segments(x["25%",], y, x["75%",], y, col = scales::alpha("royalblue", 0.5))
  } 
}

junk = sapply(1:nrow(mp), function(i) draw_rho_prior(rownames(rho_mean_out)[i], box_lwr[i,], box_upr[i,]))
junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = scales::alpha("royalblue", 0.55))
segments(rho_mean_out[,"10%"], mp, rho_mean_out[,"90%"], mp, col = scales::alpha("royalblue", 0.55))
points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "royalblue", lwd = 3)

### 2023-04-19 03-post-process/output-plots.Rmd

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "siw"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
  include_egg_to_parr_surv:
    label: "Include Egg-to-Parr Survival Output?"
    value: TRUE
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_process_model:
    label: "Include Misc. Process Model Output?"
    value: TRUE
  include_equiv_rates:
    label: "Include Equivilency Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---
